A new tidy data structure to support exploration and modeling of temporal data

### 2019-08-16 tsibble.Rmd
done with revision on transformation

# Data pipelines {#sec:pipeline}

@@

## Temporal transformation {#sec:timepipeline}

@@

These verbs are evocative and of simple interface. They by default look into gaps for each individual time period. Switching on the option `.full = TRUE` will fill in the full-length time span, creating fully balanced panels with respect to longitudinal data analysis.

Besides the time gap verbs, the **tidyverse** vocabulary is adapted and expanded to facilitate time series transformations, as listed in Table \@ref(tab:verb-table). The **tidyverse** suite showcases the general-purpose verbs for effectively manipulating tabular data, for example `filter()` picks observations, `select()` picks variables, and `left_join()` joins two tables. But these verbs need handling with care when used in the time series domain. A perceivable difference is summarizing variables between data frame and tsibble using `summarize()`. The former will reduce to a single summary, whereas the latter will obtain the index and their corresponding summaries. Users who are already familiar with the **tidyverse**, will experience a gentle learning curve for mastering these verbs and glide into time series analysis with low cognitive load.

Attention has been paid to warning and error handling. The principle that underpins most verbs is a tsibble in and a tsibble out, thereby striving to maintain a valid tsibble by automatically updating index and key under the hood. If the desired temporal ordering is changed by row-wise verbs, a warning is broadcast. If a tsibble cannot be maintained in the output of a pipeline module (likely occurring to column-wise verbs), for example the index is removed by selection, an error informs users of the problem and suggests alternatives. This avoids surprising users and reminds them of the time context.

@@

## Temporal visualization {#sec:ts-vis}

## Time series models {#sec:ts-models}

>>>>

# Temporal data pipelines {#sec:pipeline}

@@

## Transformation {#sec:timepipeline}

@@

These verbs are evocative and of simple interface. They by default look into gaps for each individual time period. Switching on the option `.full = TRUE` will fill in the full-length time span, creating fully balanced panels with respect to longitudinal study.

The other key verb is `index_by()`, the counterpart of `group_by()` in **dplyr**, grouping and partitioning the index only. It is most useful to be used in conjunction with `summarize()`, and thus aggregations to upper-level time resolutions will take place. This combination automatically produces new index and interval, and helps to regularize data of irregular interval.

Besides new verbs, the **dplyr** vocabulary has been adapted and expanded to facilitate temporal transformations. The **dplyr** suite showcases the general-purpose verbs for effectively manipulating tabular data. But these verbs need handling with care due to the context switch. A perceivable difference is summarizing variables between normal data and tsibble using `summarize()`. The former will reduce to a single summary, whereas the latter will obtain the index and their corresponding summaries. Attention has been paid to warning and error handling. The principle that underpins most verbs is a tsibble in and a tsibble out, thereby striving to maintain a valid tsibble by automatically updating index and key under the hood. If the desired temporal ordering is changed by row-wise verbs (such as `arrange()` and `slice()`), a warning is broadcast. If a tsibble cannot be maintained in the output of a pipeline module (likely occurring to column-wise verbs), for example the index is removed by `select()`-ing, an error informs users of the problem and suggests alternatives. This avoids surprising users and reminds them of the time context. In general, users who are already familiar with the **tidyverse**, should have less resistance to learning the new semantics and verbs.

## Visualization {#sec:ts-vis}

## Models {#sec:ts-models}

## Summary

@@
